\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}

%matrix one
\usepackage{dsfont}
\author{José Antonio García Hernández}
\title{4-dimensional SU(2) lattice gauge theory}
\begin{document}
\maketitle

\section{Introduction}
An SU(2) link variable is defined at a lattice point $x$ in the $\mu$ direction as $U _{\mu}(x)\in \text{SU}(2)$. An element of the group SU(2) is defined as follows

\begin{equation}
	\label{eq:SU2_element}
	U = \begin{pmatrix}
		a & b \\
		-b^* & a^*
	\end{pmatrix}
\end{equation}
where $a, \ b \in \mathbb{C}$ and $|a|^2 + |b|^2 = 1$.

\subsection{Action}
In the continuum, the action reads
\begin{equation}
	\label{eq:continuum_action}
	S[A] = \frac{1}{2g^2} \int d^4x \, \text{Tr} \left[ F_{\mu\nu}(x)F_{\mu\nu}(x)\right],
\end{equation}
where $F_{\mu\nu}(x)$ is the field strength tensor.

We defined the plaquette variable on the lattice as the ordered product of link variables on the lattice as follows
\begin{equation}
	\label{eq:plaquette}
	U_{\mu\nu}(x) = U_{\mu}(x)U_{\nu}(x+\hat{\mu})U_{\mu}^{\dagger}(x+\hat{\nu})U_{\nu}^{\dagger}(x) 
\end{equation}


On the lattice, the action takes the form
\begin{equation}
	\label{eq:wilson_action}
	S[U] = \frac{\beta}{N}\sum_x \sum_{\mu < \nu} \text{Re}\ \text{Tr} \left[\mathds{1} - U_{\mu\nu}(x) \right],
\end{equation}
where $\beta = \frac{2N}{g^2}$.

Sum of plaquette variables
\begin{equation}
	\label{eq:Sp}
	S_{\text{P}} = \frac{1}{N} \sum_x\sum_{\mu < \nu} \text{Re}\ \text{Tr} [U_{\mu\nu}(x)]
\end{equation}
we define
\begin{equation}
	\label{eq:Ep}
	E_{\text{P}} =\frac{ \langle S_{\text{P}} \rangle}{D V}
\end{equation}
where $V=L^d$ is the volume of the lattice and $D = \frac{d(d-1)}{2}$ is the number of planes of rotation.

Staples
\begin{equation}
	\label{eq:staples}
	\Sigma_{\mu}(x) = \sum_{\nu \neq \mu} \left[ U_{\nu}(x)U_{\mu}(x+\hat{\nu})U_{\nu}^{\dagger}(x+\hat{\mu}) + U_{\nu}^{\dagger}(x-\hat{\nu})U_{\mu}(x-\hat{\nu})U_{\nu}(x+\hat{\mu}-\hat{\nu})\right]
\end{equation}


The change in the action  by a local update when changing $U_{\mu}(x) \to U'_{\mu}(x)$ is
\begin{equation}
	\label{eq:DS}
	\Delta S = -\frac{\beta}{N} \text{Re } \text{Tr} \left[ \left( U'_{\mu}(x) - U_{\mu}(x) \right)\Sigma_{\mu}^{\dagger}\right].
\end{equation}

\subsection{Field strength tensor}

We can define the field strengh tensor on the lattice with either the \emph{Plaquette} or \emph{Clover} definition. A clover is defined as follows
\begin{eqnarray}
    Q_{\mu\nu}(x) & = & U_{\mu}(x)U_{\nu}(x+\hat{\mu})U_{\mu}^{-1}(x+\hat{\nu})U_{\nu}^{-1}(x)  +  \nonumber\\
    & & U_{\nu}(x)U_{\mu}^{-1}(x-\hat{\mu}+\hat{\nu})U_{\nu}^{-1}(x-\hat{\mu})U_{\mu}(x-\hat{\mu})  + \nonumber\\ 
    & & U_{\mu}^{-1}(x-\hat{\mu})U_{\nu}^{-1}(x-\hat{\mu}-\hat{\nu})U_{\mu}(x-\hat{\mu}-\hat{\nu})U_{\nu}(x-\hat{\nu})+\nonumber\\
    &  & U_{\nu}^{-1}(x-\hat{\nu}) U_{\mu}(x-\hat{\nu})U_{\nu}(x+\hat{\mu}-\hat{\nu})U_{\mu}^{-1}(x).
\end{eqnarray}

Field strength tensor with the plaquette definition
\begin{equation}
    F^{\text{plaquette}}_{\mu\nu}(x) = U_{\mu\nu}(x)
\end{equation}

Field strength tensor with the clover definition
\begin{equation}
    F^{\text{clover}}_{\mu\nu}(x) = \frac{1}{8}\left[ Q_{\mu\nu}(x) -  Q_{\mu\nu}^{\dagger}(x)\right]
\end{equation}

\subsection{Topological charge}
The topological charge $Q[U]$ of a configuration $[U]$ is defined as the sum over the lattice of the topological charge density $q(x)$ 
\begin{equation}
    q(x) = -\frac{1}{32\pi^2}\varepsilon_{\mu\nu\rho\sigma} \text{Tr} \left\{ F_{\mu\nu}(x)F_{\rho\sigma}(x)\right\}.
\end{equation}
Again, we can define the topological charge with the clover or plaquette definitions of $F_{\mu\nu}(x)$. Using the symmetries of the clover definition we can reduce the number of sums to be computed. First, we note that only 24 elements of the Levi-Civita symbol are non-zero. We also note that
\begin{eqnarray}
    \varepsilon_{\mu\nu\rho\sigma} \text{Tr} \left\{ F^{\text{clover}}_{\mu\nu}(x)F^{\text{clover}}_{\rho\sigma}(x)\right\} & = & \varepsilon_{\nu\mu\rho\sigma} \text{Tr} \left\{ F^{\text{clover}}_{\nu\mu}(x)F^{\text{clover}}_{\rho\sigma}(x)\right\} \\
    \varepsilon_{\mu\nu\rho\sigma} \text{Tr} \left\{ F^{\text{clover}}_{\mu\nu}(x)F^{\text{clover}}_{\rho\sigma}(x)\right\} & = & \varepsilon_{\mu\nu\sigma\rho} \text{Tr} \left\{ F^{\text{clover}}_{\mu\nu}(x)F^{\text{clover}}_{\sigma\rho}(x)\right\} \\
    \varepsilon_{\mu\nu\rho\sigma} \text{Tr} \left\{ F^{\text{clover}}_{\mu\nu}(x)F^{\text{clover}}_{\rho\sigma}(x)\right\} & = & \varepsilon_{\rho\sigma\mu\nu} \text{Tr} \left\{F^{\text{clover}}_{\rho\sigma} (x)F^{\text{clover}}_{\mu\nu}(x)\right\}
\end{eqnarray} 
This reduces the number of effective sums by a factor of 8. From the original 24 sums we only need to perform 3.

Using $Q$ instead of $F$ we arrive at
\begin{equation}
    \text{Tr}\{F^{\text{clover}}_{\mu\nu}(x)F^{\text{clover}}_{\rho\sigma}(x)\} =\frac{1}{2^5} \text{Tr}\left\{Q_{\mu\nu}(x)[Q_{\rho\sigma}(x)-Q_{\rho\sigma}^{\dagger}(x)]\right\}
\end{equation}
We choose the 3 independent permutations of $\varepsilon_{\mu\nu\rho\sigma}$ to be in the indices $[1,2,3,4]$, $[1,3,2,4]$ and $[1,4,2,3]$. Therefore,
\begin{equation}
    q^{\text{clover}}(x) = -\frac{1}{128 \pi^2} \sum_{[\mu\nu\rho\sigma] \in\{ [1234], [1324], [1423]\}}
              \varepsilon_{\mu\nu\rho\sigma}\text{Tr}(Q_{\mu\nu}[Q_{\rho\sigma}-Q_{\rho\sigma}^{\dagger}]) 
\end{equation}

\section{Local update algorithms}

We implemented three local update algorithms, namely, Metropolis, Glauber and Heathbath.

\subsection{Metropolis}
\begin{enumerate}
	\item Given some gauge field configuration, we go through all the lattice points in a lexicographic way. At each point $x$ in the $\mu$ direction we generate a random SU(2) matrix $U'_{\mu}(x)$.
	
	\item We compute the sum of the staples and compute the change of the action according to eq.\ \eqref{eq:DS}. We generate a uniform random number $r\in [0,1)$ and accept the change if $r \leq p$, where $p$ is
	\begin{equation}
		p = \min (1, \exp(-\Delta S)).
\end{equation}	 
\end{enumerate}

\subsection{Glauber}
\begin{enumerate}
	\item Given some gauge field configuration, we go through all the lattice points in a lexicographic way. At each point $x$ in the $\mu$ direction we generate a random SU(2) matrix $U'_{\mu}(x)$.
	
	\item We compute the sum of the staples and compute the change of the action according to eq.\ \eqref{eq:DS}. We generate a uniform random number $r\in [0,1)$ and accept the change if $r \leq p$, where $p$ is
	\begin{equation}
		p = \frac{1}{e^{\Delta S} + 1}.
\end{equation}	 
\end{enumerate}

\subsection{Heatbath}\label{sec:heatbath}
In the heatbath algorithm we need to generate an update $X\in\text{SU}(2)$
	 \begin{equation}
	 	X = \begin{pmatrix}
	 		 x_0 + ix_1 & x_2 + ix_3 \\
	 		-x_2 + ix_3 & x_0 - ix_3
	 	\end{pmatrix}
	 \end{equation}
	 where $x_0, x_1, x_2,x_3 \in \mathbb{R}$
 following the distribution
\begin{equation}
	dP(X) = \frac{1}{2\pi^2} d\cos\theta\, d\varphi\, dx_0\, \sqrt{1-x_0^2}e^{\alpha\beta x_0}
\end{equation}
\begin{enumerate}
\item Given some field configuration at a point $x$ and direction $\mu$, we compute the sum of staples $\Sigma_{\mu}(x)$ in eq.\ \eqref{eq:staples}, $\alpha = \sqrt{\det \Sigma_{\mu}(x)}$, and define $V = \Sigma_{\mu}(x)/\alpha$
	\item We generate $X$ as follows:
	\begin{enumerate}
	\item	We generate three random numbers $u_i$, $i = 1,\ 2,\ 3$ in the interval [0,1) uniformly distributed and take $r_i = 1 - u_i$. Then
		 \begin{equation}
		 	\lambda^2 = -\frac{1}{2\alpha\beta}\left(\log(r_1) + \cos^2(2\pi r_2)\log(r_3)\right).
		 \end{equation}
	\item We accept the value of $\lambda$ which obey
		\begin{equation}
			s^2 \leq 1- \lambda^2,
		\end{equation}
		where $s$ is a uniformly distributed random number in the interval [0,1).
	\item Repeat the previous two steps until a value of $\lambda$ is accepted. The accepted value gives $x_0 = 1 - 2\lambda^2$.
	\item We take the norm of the vector $\vec{x} = (x_1,x_2,x_3)$ as $|\vec{x}| = \sqrt{1 - x_0^2}$.
	\item We take two uniformly distributed random numbers $t \in [0,1)$ and $\varphi\in [0,2\pi)$ 
	\begin{eqnarray}
		x_1 & = & 1 - 2 t \\
		x_2 & = & \sqrt{1 - x_1^2} \cos\varphi \\
		x_3 & = & \sqrt{1 - x_1^2} \sin\varphi	
	\end{eqnarray}		
	  
	\end{enumerate}
	\item Once $X$ is generated, the new link variable is $U = X V$.
\end{enumerate}


\section{Smoothing procedures}

In order to compute the topological charge, we first need to smooth the configuration. This can be achived by various methods. We describe a few.

\subsection{Gradient Flow}
\begin{equation}
    \frac{d}{dt}V_{\mu}(x,t) = Z_{\mu}(x,t)V_{\mu}(x,t) , \ \ \  \left. {V_{\mu}(x,t)}\right|_{t = 0} = U_{\mu}(x)
\end{equation}

\begin{equation}
         Z_{\mu}(x) = -\{U_{\mu}(x)\Sigma_{\mu}^{\dagger}(x)\}_{\text{TA}}
\end{equation}

\begin{equation}
    W_{\text{TA}} = \frac{W - W^{\dagger}}{2} - \frac{\text{Tr} (W - W^{\dagger})}{2N}
\end{equation}

\begin{equation}
    V_{\mu}(x,t+\varepsilon) = \exp\{\varepsilon Z_{\mu}(x,t)\}V_{\mu}(x,t).
\end{equation}
%
%\begin{equation}
%    E(x,t) = \frac{1}{4} \hat{F}_{\mu\nu}^a(x,t) \hat{F}_{\mu\nu}^a(x,t)
%\end{equation}    


%\begin{equation}
%    \mathcal{E}(t) = t^2 \langle E(x,t)\rangle
%\end{equation}

\subsection{Cooling}
Each link is updated by
\begin{equation}
    U_{\mu}'(x) = \frac{\Sigma_{\mu}(x)}{\sqrt{\det \Sigma_{\mu}(x)}}.
\end{equation}
\subsection{APE smearing}
Each link is updated by 
\begin{equation}
    U_{\mu}'(x) = (1-\alpha)U_{\mu}(x)+ \frac{\alpha}{6}\Sigma_{\mu}(x).
\end{equation}
with $0<\alpha\leq 0.75$. We chose $\alpha = 0.55$.

\section{Results}
\end{document}
